\documentclass[11pt,a4paper]{article}

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------
% 0.65in margins for the "Sweet Spot"
\usepackage[left=0.65in,top=0.65in,right=0.65in,bottom=0.65in]{geometry} 
\usepackage[T1]{fontenc}  % Fixes the vertical bar issue
\usepackage{enumitem}     
\usepackage[hidelinks]{hyperref}     
\usepackage{helvet}       

% Set default font to Sans-Serif
\renewcommand{\familydefault}{\sfdefault}

%----------------------------------------------------------------------------------------
%   CUSTOM COMMANDS
%----------------------------------------------------------------------------------------
% Relaxed Section Headers
\newcommand{\resumesection}[1]{
    \vspace{1.2em} 
    {\large \textbf{\uppercase{#1}}}
    \vspace{0.2em}
    \hrule
    \vspace{0.6em} 
}

% Unified Experience Block
\newcommand{\jobrole}[4]{
    \noindent
    \textbf{#1} \hfill #3 \\ 
    \textit{#4} \hfill \textit{#2}
    \vspace{0.3em} 
}

% Relaxed Lists
\newenvironment{achievements}{
    \begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=2pt, parsep=0pt]
}{
    \end{itemize}
    \vspace{0.6em} 
}

\begin{document}

%----------------------------------------------------------------------------------------
%   HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\Large \textbf{Kumar M}} \\ \vspace{0.4em}
    % Using \vert for the vertical separator
    \small{Bengaluru, India \ $\vert$ \ +91 9486505104 \ $\vert$ \ \href{mailto:m.kumar.in@outlook.com}{m.kumar.in@outlook.com} \ $\vert$ \ \href{https://www.linkedin.com/in/kumar-mohan}{linkedin.com/in/kumar-mohan}}
\end{center}

%----------------------------------------------------------------------------------------
%   PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\resumesection{Professional Summary}
Senior System Software Engineer with \textbf{7+ years} of experience in SoC Board Bring-ups, BSP Development and Silicon Enablement. Expert in bridging the gap between hardware and software through Post-Silicon Validation and Host-Side Automation Tooling (Python/C). Proven track record of delivering mission-critical drivers for Satellite systems and Automotive ECUs.

%----------------------------------------------------------------------------------------
%   TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\resumesection{Technical Skills}
\begin{itemize}[leftmargin=1.5em, itemsep=2pt, topsep=0pt]
    \item \textbf{Languages:} Embedded C, Python, C++, Assembly, Data Structures \& Algorithms.
    \item \textbf{Hardware:} ARM Cortex-M (M0+/M4/M7), SoC Bring-up, Hardware-Software Co-design, JTAG/SWD.
    \item \textbf{System:} RTOS (FreeRTOS), Device Drivers (UART, SPI, I2C, GPIO, DMA), BSP, Power Management.
    \item \textbf{Tools:} Keil, IAR, GCC, pyOCD, Git, Jenkins, Oscilloscopes, Logic Analyzers.
\end{itemize}

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------
\resumesection{Experience}

% --- Company 1 ---
\jobrole{Microchip Technology}{Bengaluru}{May 2024 -- Present}{Senior Engineer - I, Development Tools}
\begin{achievements}
    \item Architected a generic \textbf{Python Validation Framework (pyOCD) from scratch} to automate Flash Loader verification for the \textbf{entire Microchip portfolio} (Keil \& IAR). Transformed a manual, per-family testing process into a scalable pipeline, \textbf{reducing validation cycle time by 60\%}.
    \item Delivered \textbf{Platform Enablement Firmware} (CMSIS-Pack/Flash Loaders) for multiple \textbf{ARM Cortex-M0+ families} for critical partner ecosystems (Keil MDK, IAR EWARM).
    \item Scaled validation coverage to \textbf{800+ microcontroller variants} by deploying the custom Python framework, successfully identifying and fixing critical driver regressions before public release.
\end{achievements}

% --- Company 2 ---
\jobrole{Bosch Global Software Technologies}{Bengaluru}{September 2022 -- May 2024}{Senior Engineer - I, Customer Engineering - BMW} 
\begin{achievements}
    \item Optimized thermal management and power control logic for automotive ECUs using PI loops, modeled critical paths with ASCET.
    \item Ensured \textbf{ISO 26262 compliance} by verifying Unit Tests and System Functional Tests for safety-critical modules.
    \item Optimized firmware memory usage for resource-constrained targets, reducing \textbf{HEX file size and RAM footprint} through custom linker script modifications (Awarded 1st Place in BU level Hackathon).
\end{achievements}

% --- Company 3 ---
\jobrole{Data Patterns (India) Limited}{Chennai}{December 2018 -- September 2022}{Embedded Software Engineer}
\begin{achievements}
    \item Engineered \textbf{Mission-Critical Bare-Metal Firmware} for ISRO (INS-2TD) and Pixxel satellites. Delivered low-latency drivers for Telemetry (UART/I2C) and Reaction Wheels under strict timing constraints.
    \item Led \textbf{Board Bring-up \& Schematic Verification} for Avionics hardware (LCA Tejas). Resolved \textbf{Signal Integrity} and power sequencing issues using Oscilloscopes and Logic Analyzers.
    \item \textbf{Awarded ISRO Recognition:} Received accolades from LEO Directors for contributions to INS-2TD satellite mission.
\end{achievements}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\resumesection{Education}
\noindent
\textbf{Bachelor of Engineering (Electronics \& Communication)} \hfill 2014 -- 2018 \\
\textit{Anna University, Chennai} % FIXED: Added closing brace here

\end{document}
